Deliminative verbal reduplication in Mandarin Chinese

### 2025-06-14 replies-reviews2.tex

\item p. 15, lines 25--28: ``\textit{Le} is compatible with the reduplication, because its dynamicity can relate to not
only the termination or instantiation of an event (a point of change), but also the process of the
situation, just like that of the reduplication (see Section 2.3.1)''. This passage is unclear. Please revise
it for clarity.

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
\noindent
\textbf{Answer:} This passage is revised as follows 
and moved before example (28) to directly follow the passage before: 
``As shown in Section 2.3.1, reduplication can also express
 dynamicity of both a time point and a time period, 
 just like \obj{le} illustrated here. 
 Therefore, \obj{le} is compatible with reduplication.''

\item P. 16, lines 31--34: ``A reviewer also notes that the reduplication appears frequently in imperative
(example 25a) and conditional sentences (31) as well as causative sentences with \pinyin{rang4/jiao4/shi3}
`let/let/make' (examples 21, 22, 25c).''
This is not exactly what the reviewer stated. The reviewer was not referring to reduplicated verbs in
general. Rather, s/he noted that, as described in various grammars, verbs depicting events not
controlled by an agent (which normally cannot be reduplicated) sometimes undergo reduplication,
especially in imperative, conditional, or causative sentences. I am not sure if reduplication, in general,
tends to appear specifically in these sentence types. It seems to me that it appears frequently in other
contexts as well. The claim ``This explains the general tendency for reduplication to appear in
conditional clauses, imperative, or causative contexts, frequently describing future situations'' (p. 17,
lines 4--6) should be reconsidered.

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
\noindent
\textbf{Answer:} This passage is removed. 
Instead, a footnote is added to Section 2.3.2 at the discussion on 
the reduplication of non-volitional verbs in example (18) (example (17) in the previous draft): 
``A reviewer notes that verbs depicting events not controlled 
by an agent sometimes can undergo reduplication, 
especially in imperative, conditional, or causative sentences. 
It is worthwhile to delve into why such sentence structures
 enable reduplication for these verbs. 
 It is also worth noting that the sentences in (18) 
 are not imperative, conditional or causative sentences. 
 This shows that non-volitional verbs can also be reduplicated
  outside of the aforementioned sentence structures''.

@@

Be careful: stating that reduplication is a syntactic phenomenon does not mean it is an instance of
repetition. Arguing that diminishing reduplication is a syntactic phenomenon affecting the vP domain
and proposing a syntactic analysis (as in \citealt{Arcodiaetal2014} and \citealt{BascianoMelloni2017}) does not imply that it is syntactic repetition; they are two different phenomena.

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
\noindent
\textbf{Answer:} We do not claim that the syntactic analyses consider reduplication to be repetition. We added a footnote to clarify this point.

\item p.23, lines 29--31: ``Third, idioms (52a) lose their idiomatic meaning when used with verbal classifiers
(52b) but maintain their idiomatic meaning with reduplications (52c) \citep[230--231]{YangWei2017}.''
It would be useful to specify that this applies except when 一下 \textit{yixia} is used, which indicates short
duration.

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
\noindent
\textbf{Answer:} We modified footnote 14 (footnote 11 in the previous draft) as follows to make this point clearer: ``This applies except when \obj{yi2 xia4} `once' is used. Because of this exception, one reviewer suggests that the lost of the idiomatic interpretation may be attributed to the use of the numeral \obj{san1} `three' in (52b). We suggest that it is not \obj{san1} \obj{xia4} `three times' that is special, 
but it is \obj{yi2} \obj{xia4} `once' that is special.
We can replace \obj{san1} `three' with any number above two,
and the distinction still exist.
But \obj{yi2} \obj{xia4} `once' has acquired a duration reading `for a little while' that is not available to the other event quantifiers formed by \obj{xia4}, which only have the `for X times' interpretation (\citealt[77]{Deng2013}, \citealt[16]{Zhang2000}).
We think \obj{liang3} \obj{xia4} `twice' is following this tendency, too.
In this case, it is easy to interpret \obj{yi2} \obj{xia4} and \obj{liang3} \obj{xia4} not as referring to the actual number of action taking place,
but as duration adverbials as a whole,
thus differing them from ``actual'' verbal classifier phrases with other numerals''.

@@

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
\noindent
\textbf{Answer:} We corrected this.

\item P. 26, lines 27--28: ``He observes that \textit{zhe} `PROG', \textit{le} `PFV' and \pinyin{wan2} `COMPL' necessarily occur
with additional information about the event denoted by the sentence (53), while \pinyin{zai4} `dur' and \pinyin{guo4}
`EXP' can occur without further information (54).''

This passage is not completely clear. Please revise and clarify it. Also, the aspect marker 过 \textit{guo}
should be toneless.

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
\noindent
\textbf{Answer:} We modified the passage as follows and added more examples to make it clearer: 
``He observes the so-called incompleteness effect, namely that a minimal sentence, 
which only contains a verb marked by \obj{zhe} `\textsc{dur}',
\obj{le} `\textsc{pfv} or \obj{wan2} \textsc{compl} 
and its arguments, 
seems incomplete without further sentential elements 
such as the sentence final particle \obj{le} 
or a temporal adverbial like \obj{gang1cai2} `just now' (51) . 
In contrast, a minimal sentence with a verb marked by  \obj{zai4} `prog' or \obj{guo}
`\textsc{exp}'  and its arguments can stand alone (52).''

@@

    We recognize these uses require specific context information.

    \item On Page 20, the authors use the modification test \citep{Dai1992} to argue that verb reduplication behaves like words rather than phrases. Example (43) illustrates that adverbs cannot be inserted within a verb reduplication. However, this argument could be strengthened by addressing the following point: The rationale for inserting the adverb within the reduplication is not very clear. Even for typical verb phrases like 开门 \textit{kāi mén} (`open the door'), adverbs cannot be inserted between the verb and its
    object (e.g., 开偷偷地门 \textit{kāi tōutōu de mén} `open the door secretly' is ungrammatical).
    This suggests that the inability to insert an adverb is not unique to reduplication and may not prove its word-like property.

    %%%%%%%%%%%%%%%%%%%
    %%%%%%%%%%%%%%%%%%%
    \noindent
    \textbf{Answer:} The rationale for inserting an adverb in-between the reduplication is that a verb can be modified by an adverb, hence the modification test.
    In Mandarin Chinese, almost all adverbials are obligatorily pre-verbal \citep[50]{Ernst2014}, as illustrated in the example below (\ref{ex:adv}).
    \ea\label{ex:adv}
    \ea[]{\gll \objex{ta1} \objex{qiao1qiao1de} \objex{zou3-le}\\
    he quietly go-\textsc{pfv}.\\
    \glt `He quietly went away.'
    }
    \ex[*]{\gll \objex{ta1} \objex{zou3-le} \objex{qiao1qiao1de}.\\
    he go-\textsc{pfv} quietly\\
    }
    \z\z
    Therefore, the general explanation for the ungrammaticality of \obj{kai1} \obj{tou1tou1de} \obj{men2} `open secretly door' is that the adverb cannot occur after the verb.
    This is not a problem for the test in (43), as the adverb can, in principle, be interpreted as modifying the second verb.

  \citet[50]{Ernst2014} mentions that the only possible post-verbal adverbials are participant PPs (\textit{with somebody}),
  manner or resultative V-de constructions as well as 
  duration and frequency expressions.
  (\ref{ex:VPinsert}) shows a case of inserting a frequency expression into a VP.
  This suggests that it is, in principle, possible to insert adverbials into a VP.

  \ea\label{ex:VPinsert}
    \gll \objex{kai1}  \objex{san3} \objex{ci4} \objex{men2}\\
    open three time door\\
    \glt `open the door three times'
  \z
